Parallel algorithm for solving multicriterial optimization problems using elements of machine learning

### 2025-06-13 2025/RSCD_MCO/RSD-2025.tex
1. поправил подпись fig.2 2. Добавил описание экспериментов раздел 5

\begin{figure}
\center
\includegraphics[width=0.6\textwidth]{fig2.png}
\caption{Example of Pareto set evaluation in solving two scalar optimization problems (values in the domain of criteria values).} \label{fig2}
\end{figure}

@@

Fig. \ref{fig5} shows the dependence of the average value of the HV index on the average number of trials for the sequential algorithm. Several solution accuracy values $\varepsilon = \{0.1,0.05,0.01\}$ were fixed for plotting the graph for algorithm (\ref{eq:13}). 100 problems were solved for each accuracy value and the average results were plotted on a graph. The position of the resulting curve for the chosen algorithm to the left and above corresponds to the best behavior of the algorithm as a whole. During the experiments the parameter $\alpha$ from (15) varied, Fig. \ref{fig5} shows only the best results for each of the variants.

>>>>

\begin{figure}
\center
\includegraphics[width=0.6\textwidth]{fig2.png}
\caption{Example of Pareto set evaluation in solving two scalar optimization problems (trial values are presented in the criterion value range).} \label{fig2}
\end{figure}

@@

Fig. \ref{fig5} shows the dependence of the average value of the HV index on the average number of trials for the sequential algorithm. The number of $\lambda$ values from (\ref{eq:04}) in all experiments was equal to $\tau=50$. The $\lambda$ values were chosen to be uniformly distributed over the interval [0,1]. Several solution accuracy values $\varepsilon = \{0.1,0.05,0.01\}$ were fixed for plotting the graph for algorithm (\ref{eq:13}). 100 problems were solved for each accuracy value and the average results were plotted on a graph. The position of the resulting curve for the chosen algorithm to the left and above corresponds to the best behavior of the algorithm as a whole. During the experiments the parameter $\alpha$ from (15) varied, Fig. \ref{fig5} shows only the best results for each of the variants.
